---
title: "Adiposity and biological age in CLHNS - Figures"
author: "Remy Voloshchuk"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, eval=TRUE, include=TRUE, cache=FALSE)
devtools::load_all()
library(BAA)
library(jtools)
library(ggplot2)
library(ggpubr)
library(cowplot)
library(patchwork)
library(tidyr)
library(kableExtra)
library(modelsummary)
library(openxlsx)
library(dplyr)
library(survey)
library(gtsummary)
```

```{r load data, eval=TRUE, include=FALSE}

load('../data.RData')

# scaling WC, WHtR, and DunedinPACE, DNAmTL residual by 10
epi4 <- epi_deid2 %>% mutate_at(vars(c(whtr, r.dnamtl)), ~ 10*.) %>% mutate(waist = waist/10) %>% mutate(bmi = bmi/5) %>%
  # scaling other residuals to be in months
  mutate_at(vars(c(r.dnamage, r.dnamagehannum, r.dnamphenoage, r.dnamgrimage, r.pchorvath2, r.pchannum, r.pcphenoage, r.pcgrimage)), ~ 12*.) %>%
  # scaling DunedinPACE to report it in weeks
  mutate_at(vars(dunedin), ~ 100*.)

my_betas = c("BMI", "WC", "WHtR", 
             "Sex", "uw",
             paste0("BMI", "*Sex"), paste0("WC", "*Sex"), paste0("WHtR", "*Sex"), 
             paste0("BMI", "*uw"), paste0("WC", "*uw"), paste0("WHtR", "*uw"))

```

## Tables {.tabset .tabset-fade .tabset-pills}

### Table 1 (main and supplementary) {.tabset .tabset-fade .tabset-pills}

#### Table 1 (main)

For main text

```{r table 1 main, eval=TRUE, message=FALSE, warning=FALSE, include=TRUE}

# adding and comparing them
epi_deid2.t1 <- epi_deid2 %>% mutate(across(sex, as.numeric)) # getting rid of labels

#####
# making table to beautifully share info
epi_deid2.t1_svy <- svydesign(id      = ~new_ids,
                          data    = epi_deid2.t1 %>% mutate(
                            sex = case_when(
                              sex == 1 ~ "Female",
                              sex == 2 ~ "Male", TRUE ~ NA
                            ),
                            cursmok = case_when(
                              cursmok == 1 ~ 'Never',
                              cursmok == 2 ~ 'Former',
                              cursmok == 3 ~ 'Current'
                            ),
                            cat.preg.comp = case_when(
                              num.preg.comp == 1 ~ "1",
                              num.preg.comp == 2 ~ "2",
                              num.preg.comp > 2  ~ "3+",
                              sex == 2            ~ NA,
                              TRUE ~ "0"
                            ),
                            totmonthsbf = case_when(
                              num.preg.comp == 0 ~ NA,
                              sex == 2           ~ NA,
                              TRUE ~ totmonthsbf
                              ),
                            nobf = case_when(
                              sex == 2          ~ NA,
                              totmonthsbf > 0   ~ "Yes",
                              num.preg.comp > 0 ~ "No",
                              TRUE ~  NA
                              )
                            ) %>% mutate(
                              nobf = factor(nobf, levels = c("Yes", "No")),
                              cat.preg.comp = factor(cat.preg.comp, levels = c("0", "1", "2", "3+")),
                              cursmok = factor(cursmok, levels = c("Current", "Former", "Never"))
                            )
                         )

#####
sum.table <- tbl_svysummary(data = epi_deid2.t1_svy, 
                 by =  sex,
    # Use include to dplyr::select variables
    include = c(height, weight, bmi, f.bmi4cat,
                waist, f.waist.high,
                whtr, f.whtr.high,
                # clocks
                r.dnamage, r.dnamagehannum, r.dnamphenoage, r.dnamgrimage, r.dnamtl, dunedin,
                r.pchorvath2, r.pchannum, r.pcphenoage, r.pcgrimage, r.pcdnamtl, factor.age, pcfactor.age,
                # covariates
                hai, cursmok
                ), 
   label = list(height ~ "Height (cm)",
                weight ~ "Weight (kg)",
                waist ~ "Waist (cm)",
                f.waist.high ~ "Waist Circumference Category",
                whtr ~ "Waist-to-height ratio",
                f.whtr.high ~ "Waist-to-Height Ratio Category",
                bmi ~ "BMI (kg/m2)",
                f.bmi4cat ~ 'BMI Category',
                # clocks
                r.dnamage ~ "Horvath", 
                r.dnamagehannum ~ "Hannum", 
                r.dnamphenoage ~ "PhenoAge", 
                r.dnamgrimage ~ "GrimAge", 
                r.dnamtl ~ "DNAmTL", 
                dunedin ~ "DunedinPACE",
                r.pchorvath2 ~ "PCHorvath", 
                r.pchannum ~ "PCHannum", 
                r.pcphenoage ~ "PCPhenoAge", 
                r.pcgrimage ~ "PCGrimAge", 
                r.pcdnamtl ~ "PCDNAmTL",
                factor.age ~ "Factor", 
                pcfactor.age ~ "PCFactor",
                # covariates
                hai ~ "Household Wealth Index", 
                cursmok ~ "Smoking Status"),
    statistic = list(all_continuous()  ~ "{mean} ({sd})",
                     all_categorical() ~ "{n}  ({p}%)"),
    digits = list(all_continuous()  ~ c(1, 1),
                  c(r.dnamage, r.dnamagehannum, r.dnamphenoage, r.dnamgrimage, r.dnamtl, dunedin,
                    r.pchorvath2, r.pchannum, r.pcphenoage, r.pcgrimage, r.pcdnamtl, factor.age, pcfactor.age, hai, whtr) ~ c(3,3),
                  all_categorical() ~ c(0, 1)),
    type = list(c(height, weight, bmi, waist, whtr,
                  r.dnamage, r.dnamagehannum, r.dnamphenoage, r.dnamgrimage, r.dnamtl, dunedin,
                  r.pchorvath2, r.pchannum, r.pcphenoage, r.pcgrimage, r.pcdnamtl, hai, factor.age, pcfactor.age) ~ "continuous"),
   # sort = list(c(colnames(epi_deid2.t1_svy)[grepl(".high", epi_deid2.t1_svy %>% colnames)], cursmok) ~ "frequency"),
    missing = "no"
  ) %>%
  modify_caption("Descriptive statistics") %>%
  add_p(test = list(
      all_continuous() ~ "svy.kruskal.test",
      all_categorical() ~ "svy.chisq.test"
    )
  )%>%
  bold_labels()%>%
    add_overall(
    #statistic = ~"(n={n_unweighted}"
      )%>%
      modify_header(label = "**Variable**", all_stat_cols() ~ "**{level}**, n = {n} ({style_percent(p)}%)")

# write.csv2(sum.table %>% as.data.frame(), "tables/table1.csv")

sum.table
```

#### Table 1 (pregnancy + breastfeeding variables)

For females, add to main later

```{r table 1 fem, eval = TRUE, include = TRUE}

# adding and comparing them
epi_deid2.t1f <- epi_deid2 %>% filter(sex==0) %>% mutate(across(sex, as.numeric)) # getting rid of labels

epi_deid2.t1_svyf <- svydesign(id      = ~new_ids,
                          data    = epi_deid2.t1f %>% mutate(
                            cat.preg.comp = case_when(
                              num.preg.comp == 1 ~ "1",
                              num.preg.comp == 2 ~ "2",
                              num.preg.comp > 2  ~ "3+",
                              sex == 2            ~ NA,
                              TRUE ~ "0"
                            ),
                            totmonthsbf = case_when(
                              num.preg.comp == 0 ~ NA,
                              sex == 2           ~ NA,
                              TRUE ~ totmonthsbf
                              ),
                            nobf = case_when(
                              sex == 2          ~ NA,
                              totmonthsbf > 0   ~ "Yes",
                              num.preg.comp > 0 ~ "No",
                              TRUE ~  NA
                              )
                            ) %>% mutate(
                              nobf = factor(nobf, levels = c("Yes", "No")),
                              cat.preg.comp = factor(cat.preg.comp, levels = c("0", "1", "2", "3+"))
                            )
                          )

#####
sum.table.f <- tbl_svysummary(data = epi_deid2.t1_svyf, 
    # Use include to dplyr::select variables
    include = c(cat.preg.comp, nobf, totmonthsbf
                ), 
   label = list(cat.preg.comp ~ "Completed Pregnancies", 
                nobf ~ "Ever breastfed?", 
                totmonthsbf ~ "Total months breastfeeding"),
    statistic = list(all_continuous()  ~ "{mean} ({sd})",
                     all_categorical() ~ "{n}  ({p}%)"),
    digits = list(all_continuous()  ~ c(1, 1),
                  all_categorical() ~ c(0, 1)),
    type = list(c(totmonthsbf) ~ "continuous"),
   # sort = list(c(colnames(epi_deid2.t1_svy)[grepl(".high", epi_deid2.t1_svy %>% colnames)], cursmok) ~ "frequency"),
    missing = "no"
  ) %>%
  modify_caption("Descriptive statistics") %>%
  bold_labels()%>%
      modify_header(label = "**Variable**", all_stat_cols() ~ "**{level}**, n = {n} ({style_percent(p)}%)")

# write.csv2(sum.table.f %>% as.data.frame(), "tables/table1_f.csv")
sum.table.f

```

### Making models with standardised betas {.tabset .tabset-fade .tabset-pills}

```{r making models 1, include = FALSE, eval = TRUE}

# create empty lists
# non-PC clocks
all.unadj.i <- list() # unadjusted, except for sex, interacted with exposure
all.adj2 <- list() # fully-adjusted
all.adj3 <- list() # fully-adjusted, with underweight interacted
all.adj4 <- list() # fully-adjusted, without uw interactions, not sex-stratified
all.adj5 <- list() # fully-adjusted, without interactions

# PC clocks
all.pc.unadj.i <- list() # unadjusted, except for sex, interacted with exposure
all.pc.adj2 <- list() # fully-adjusted
all.pc.adj3 <- list() # fully-adjusted, with underweight interacted
all.pc.adj4 <- list() # fully-adjusted, without uw interactions, not sex-stratified
all.pc.adj5 <- list() # fully-adjusted, without interactions

for (j in 1:length(exposures)) {
  all.unadj.i[[j]] <- table.mvreg(mvreg_response_ns_nonpc, exposures[j], c(paste0(exposures[j], "*sex")), epi4, to_return = "model")
  all.adj2[[j]] <- table.mvreg(mvreg_response_ns_nonpc, exposures[j], c(paste0(exposures[j], "*sex"), cell.props, covars.fem), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, not uw-stratified
  all.adj3[[j]] <- table.mvreg(mvreg_response_ns_nonpc, exposures[j], c(cell.props, covars.fem, paste0(exposures[j], "*sex"), paste0(exposures[j], "*uw")), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, with sex and uw interactions, not sex-stratified
  all.adj4[[j]] <- table.mvreg(mvreg_response_ns_nonpc, exposures[j], c(cell.props, covars.fem, "sex", paste0(exposures[j], "*uw")), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, without sex interactions, with uw interaction
  all.adj5[[j]] <- table.mvreg(mvreg_response_ns_nonpc, exposures[j], c(cell.props, covars.fem, "sex"), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, without interactions
}

# adding height to the waist circumference plots.
all.adj2[[2]] <- table.mvreg(mvreg_response_ns_nonpc, exposures[2], c(paste0(exposures[2], "*sex"), cell.props, covars.fem, "height*sex"), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, not uw-stratified
all.adj3[[2]] <- table.mvreg(mvreg_response_ns_nonpc, exposures[2], c(cell.props, covars.fem, paste0(exposures[2], "*sex"), paste0(exposures[2], "*uw"), "height*sex"), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, with sex and uw interactions, not sex-stratified
all.adj4[[2]] <- table.mvreg(mvreg_response_ns_nonpc, exposures[2], c(cell.props, covars.fem, paste0(exposures[2], "*uw"), "height*sex"), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, without sex interactions, with uw interaction
all.adj5[[2]] <- table.mvreg(mvreg_response_ns_nonpc, exposures[2], c(cell.props, covars.fem, "height*sex"), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, without interactions

for (j in 1:length(exposures)) {
  all.pc.unadj.i[[j]] <- table.mvreg(mvreg_response_ns_pc, exposures[j], c("sex", paste0(exposures[j], "*sex")), epi4, to_return = "model")
  all.pc.adj2[[j]] <- table.mvreg(mvreg_response_ns_pc, exposures[j], c(paste0(exposures[j], "*sex"), cell.props, covars.fem), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, not uw-stratified
  all.pc.adj3[[j]] <- table.mvreg(mvreg_response_ns_pc, exposures[j], c(paste0(exposures[j], "*sex"), cell.props, covars.fem, paste0(exposures[j], "*sex"), paste0(exposures[j], "*uw")), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, with sex and uw interactions, not sex-stratified
  all.pc.adj4[[j]] <- table.mvreg(mvreg_response_ns_pc, exposures[j], c(cell.props, covars.fem, "sex", paste0(exposures[j], "*uw")), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, without sex interactions, with uw interaction
  all.pc.adj5[[j]] <- table.mvreg(mvreg_response_ns_pc, exposures[j], c(cell.props, covars.fem, "sex"), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, without interactions
}

# adding height to the waist circumference plots.
all.pc.adj2[[2]] <- table.mvreg(mvreg_response_ns_pc, exposures[2], c(paste0(exposures[2], "*sex"), cell.props, covars.fem, "height*sex"), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, not uw-stratified
all.pc.adj3[[2]] <- table.mvreg(mvreg_response_ns_pc, exposures[2], c(cell.props, covars.fem, paste0(exposures[2], "*sex"), paste0(exposures[2], "*uw"), "height*sex"), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, with sex and uw interactions, not sex-stratified
all.pc.adj4[[2]] <- table.mvreg(mvreg_response_ns_pc, exposures[2], c(cell.props, covars.fem, paste0(exposures[2], "*uw"), "height*sex"), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, without sex interactions, with uw interaction
all.pc.adj5[[2]] <- table.mvreg(mvreg_response_ns_pc, exposures[2], c(cell.props, covars.fem, "height*sex"), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, without interactions

```

```{r which model 5 u}

num <- length(exposures)*length(mvreg_response_labels)

all.final <- list(list(),list(),list(),list())

all.pc.final <- list(list(),list(),list(),list())

for (i in 1:length(exposures)) {
  for (j in 1:length(mvreg_response_labels)) {
    all.final[[i]][[j]] <- return.fm(return.fm(all.adj3[[i]][[j]], all.adj2[[i]][[j]], all.adj5[[i]][[j]]), return.fm(all.adj3[[i]][[j]], all.adj4[[i]][[j]], all.adj5[[i]][[j]]))
  
    all.pc.final[[i]][[j]] <- return.fm(return.fm(all.pc.adj3[[i]][[j]], all.pc.adj2[[i]][[j]], all.pc.adj5[[i]][[j]]), return.fm(all.pc.adj3[[i]][[j]], all.pc.adj4[[i]][[j]], all.pc.adj5[[i]][[j]]))
  }
}

```

```{r making sex-stratified models for DunedinPACE, include = FALSE}

# create empty lists
# males
m.adj2 <- list() # fully-adjusted
m.adj3 <- list() # fully-adjusted, with underweight interacted

# females
f.adj2 <- list() # fully-adjusted
f.adj3 <- list() # fully-adjusted, with underweight interacted

# Male only
for (j in 1:length(exposures)) {
  m.adj2[[j]] <- table.mvreg(mvreg_response_ns_nonpc[7], exposures[j], c(cell.props, covars.all), epi4[epi4$sex == 1,], to_return = "model") # fully-adjusted, not underweight-interacted
  m.adj3[[j]] <- table.mvreg(mvreg_response_ns_nonpc[7], exposures[j], c(cell.props, covars.all, paste0(exposures[j], "*uw")), epi4[epi4$sex == 1,], to_return = "model") # fully-adjusted, underweight interacted
}

# adding height to waist circumference
m.adj2[[2]] <- table.mvreg(mvreg_response_ns_nonpc[7], exposures[2], c(cell.props, covars.all, "height"), epi4[epi4$sex == 1,], to_return = "model") # fully-adjusted, not underweight-interacted
m.adj3[[2]] <- table.mvreg(mvreg_response_ns_nonpc[7], exposures[2], c(cell.props, covars.all, paste0(exposures[2], "*uw"), "height"), epi4[epi4$sex == 1,], to_return = "model") # fully-adjusted, underweight interacted

# Female only
for (j in 1:length(exposures)) {
  f.adj2[[j]] <- table.mvreg(mvreg_response_ns_nonpc[7], exposures[j], c(cell.props, covars.fem), epi4[epi4$sex == 0,], to_return = "model") # fully-adjusted, not sex-stratified
  f.adj3[[j]] <- table.mvreg(mvreg_response_ns_nonpc[7], exposures[j], c(cell.props, covars.fem, paste0(exposures[j], "*uw")), epi4[epi4$sex == 0,], to_return = "model") # fully-adjusted, underweight interacted
}

# adding height to waist circumference
f.adj2[[2]] <- table.mvreg(mvreg_response_ns_nonpc[7], exposures[2], c(cell.props, covars.fem, "height"), epi4[epi4$sex == 0,], to_return = "model") # fully-adjusted, not underweight-interacted
f.adj3[[2]] <- table.mvreg(mvreg_response_ns_nonpc[7], exposures[2], c(cell.props, covars.fem, paste0(exposures[2], "*uw"), "height"), epi4[epi4$sex == 0,], to_return = "model") # fully-adjusted, underweight interacted

```

```{r which model 5 u sex-stratified}

num <- length(exposures)*length(mvreg_response_labels)

f.final <- list(list(),list(),list())
m.final <- list(list(),list(),list())

f.pc.final <- list(list(),list(),list())
m.pc.final <- list(list(),list(),list())

for (i in 1:length(exposures)) {
  f.final[[i]][[1]] <- return.fm(f.adj3[[i]][[1]], f.adj2[[i]][[1]])
  m.final[[i]][[1]] <- return.fm(m.adj3[[i]][[1]], m.adj2[[i]][[1]])
}

```

### Table 2 (Unstandardised betas, unstratified models) {.tabset .tabset-fade .tabset-pills}

#### BMI non-PC

```{r Table 2u BMI unstandardised non-PC, eval=TRUE,include=TRUE}

# BMI, non-pc
make_table2(
  model_list = list(all.unadj.i[[1]], all.adj3[[1]], all.final[[1]]),
  model_names = mvreg_response_labels,
  keep_betas = my_betas,
  kable = FALSE
  ) %>% 
  my_kable(my_header = "Non-PC Clocks | BMI",
           col.names = c("Clock", "Term", "Model 1", "Model 2", "Final"))

```

#### BMI PC

```{r Table 2u BMI standardised PC, eval=TRUE,include=TRUE}
# BMI, pc
make_table2(
  model_list = list(all.pc.unadj.i[[1]], all.pc.adj3[[1]], all.pc.final[[1]]),
  model_names = mvreg_response_labels,
  keep_betas = my_betas, 
  kable = FALSE
  ) %>% my_kable(my_header = "PC Clocks | BMI",
                 col.names = c("Clock", "Term", "Model 1", "Model 2", "Final"))

```

#### Waist Circumference non-PC

```{r Table 2u WC non-PC, eval=TRUE,include=TRUE}

# WC, non-pc
make_table2(
  model_list = list(all.unadj.i[[2]], all.adj3[[2]], all.final[[2]]),
  model_names = mvreg_response_labels,
  keep_betas = my_betas, 
  kable = FALSE
  ) %>% my_kable(my_header = "Non-PC Clocks | Waist Circumference",
                 col.names = c("Clock", "Term", "Model 1", "Model 2", "Final"))

```

#### Waist Circumference PC

```{r Table 2u WC PC, eval=TRUE,include=TRUE}
# Waist Circumference, pc
make_table2(
  model_list = list(all.pc.unadj.i[[2]], all.pc.adj3[[2]], all.pc.final[[2]]),
  model_names = mvreg_response_labels,
  keep_betas = my_betas, 
  kable = FALSE
  ) %>% my_kable(my_header = "PC Clocks | Waist Circumference",
                 col.names = c("Clock", "Term", "Model 1", "Model 2", "Final"))

```

#### Waist-to-Height Ratio non-PC

```{r Table 2u WHtR non-PC, eval=TRUE,include=TRUE}

# WHtR, non-pc
make_table2(
  model_list = list(all.unadj.i[[3]], all.adj3[[3]], all.final[[3]]),
  model_names = mvreg_response_labels,
  keep_betas = my_betas, 
  kable = FALSE
  ) %>% my_kable(my_header = "Non-PC Clocks | Waist-to-Height Ratio",
                 col.names = c("Clock", "Term", "Model 1", "Model 2", "Final"))
```

#### Waist-to-Height Ratio PC

```{r Table 2u WHtR PC, eval=TRUE,include=TRUE}
# Waist-to-Height Ratio, pc
make_table2(
  model_list = list(all.pc.unadj.i[[3]], all.pc.adj3[[3]], all.pc.final[[3]]),
  model_names = mvreg_response_labels,
  keep_betas = my_betas, 
  kable = FALSE
  ) %>% my_kable(my_header = "PC Clocks | Waist-to-Height Ratio",
                 col.names = c("Clock", "Term", "Model 1", "Model 2", "Final"))
```

### Table 2 (Unstandardised betas, for publication) {.tabset .tabset-fade .tabset-pills}

#### Individual Clocks

##### non-PC
```{r, include = TRUE}

make_table2_pub(
    model_list = all.final,
    model_names = mvreg_response_nonpc,
    keep_betas = c("BMI", "WC", "WHtR"),
    start = 2, stop = 7
) %>% my_kable(
    col.names = c(
        "Measure", "Coeff", mvreg_response_labels[2:7]
        ),
    caption = "Unstandardised Betas"
)

full_join(
  adj_benj_hoch(
    do.call(rbind, lapply(c(1:length(exposures_pub)), function(x) extract_coef_pval(
      f.final[[x]][[1]],
      model_name = exposures_pub[x],
      to_return = c("BMI", "WC", "WHtR", "BMI*uw", "WC*uw", "WHtR*uw")
    ))), which.group2 = c("BMI", "WC", "WHtR")
  ),
  adj_benj_hoch(
    do.call(rbind, lapply(c(1:length(exposures_pub)), function(x) extract_coef_pval(
      m.final[[x]][[1]],
      model_name = exposures_pub[x],
      to_return = c("BMI", "WC", "WHtR", "BMI*uw", "WC*uw", "WHtR*uw")
    ))), which.group2 = c("BMI", "WC", "WHtR")
  ), by = c("Clock", "term")
) %>% mutate(across(everything(), ~ifelse(is.na(.), "", .))) %>% kable(col.names = c("Measure", "Coeff", "Female", "Male"), format='html', escape=FALSE) %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  column_spec(column = 1, bold = TRUE) %>%
  column_spec(column = 3:4, width = "16em") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  add_header_above(header = c(
    setNames(object = 2, nm = " "),
    setNames(object = 2, nm = mvreg_response_labels[7])
    ))

```

##### PC
```{r, include = TRUE}

make_table2_pub(
    model_list = all.pc.final,
    model_names = mvreg_response_pc,
    keep_betas = c("BMI", "WC", "WHtR"),
    start = 2, stop = 7
) %>% my_kable(
    col.names = c(
        "Measure", "Coeff", mvreg_response_labels_pub[2:7]
        ),
    caption = "Unstandardised Betas"
)

```

#### Combination Clocks

```{r, include = TRUE}

make_table2_pub(
    model_list = list(list(all.final[[1]][[1]], all.pc.final[[1]][[1]]), list(all.final[[2]][[1]], all.pc.final[[2]][[1]]), list(all.final[[3]][[1]], all.pc.final[[3]][[1]])),
    model_names = mvreg_response_pc,
    keep_betas = c("BMI", "WC", "WHtR"),
    start = 1, stop = 2,
    which.group2 = "none"
) %>% my_kable(
    col.names = c(
        "Measure", "Coeff", c(mvreg_response_labels[1], mvreg_response_labels_pub[1])
        ),
    caption = "Unstandardised Betas"
)

```

### Making models with standardised betas {.tabset .tabset-fade .tabset-pills}

```{r making models 1s, include = FALSE, eval = TRUE}

# create empty lists
# non-PC clocks
all.unadj.i <- list() # unadjusted, except for sex, interacted with exposure
all.adj2 <- list() # fully-adjusted
all.adj3 <- list() # fully-adjusted, with underweight interacted
all.adj4 <- list() # fully-adjusted, without uw interactions, not sex-stratified
all.adj5 <- list() # fully-adjusted, without interactions

# PC clocks
all.pc.unadj.i <- list() # unadjusted, except for sex, interacted with exposure
all.pc.adj2 <- list() # fully-adjusted
all.pc.adj3 <- list() # fully-adjusted, with underweight interacted
all.pc.adj4 <- list() # fully-adjusted, without uw interactions, not sex-stratified
all.pc.adj5 <- list() # fully-adjusted, without interactions

for (j in 1:length(exposures.std)) {
  all.unadj.i[[j]] <- table.mvreg(mvreg_response_nonpc, exposures.std[j], c(paste0(exposures.std[j], "*sex")), epi4, to_return = "model")
  all.adj2[[j]] <- table.mvreg(mvreg_response_nonpc, exposures.std[j], c(paste0(exposures.std[j], "*sex"), cell.props, covars.fem), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, not uw-stratified
  all.adj3[[j]] <- table.mvreg(mvreg_response_nonpc, exposures.std[j], c(cell.props, covars.fem, paste0(exposures.std[j], "*sex"), paste0(exposures.std[j], "*uw")), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, with sex and uw interactions, not sex-stratified
  all.adj4[[j]] <- table.mvreg(mvreg_response_nonpc, exposures.std[j], c(cell.props, covars.fem, "sex", paste0(exposures.std[j], "*uw")), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, without sex interactions, with uw interaction
  all.adj5[[j]] <- table.mvreg(mvreg_response_nonpc, exposures.std[j], c(cell.props, covars.fem, "sex"), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, without interactions
}

# adding height to the waist circumference plots.
all.adj2[[2]] <- table.mvreg(mvreg_response_nonpc, exposures.std[2], c(paste0(exposures.std[2], "*sex"), cell.props, covars.fem, "height*sex"), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, not uw-stratified
all.adj3[[2]] <- table.mvreg(mvreg_response_nonpc, exposures.std[2], c(cell.props, covars.fem, paste0(exposures.std[2], "*sex"), paste0(exposures.std[2], "*uw"), "height*sex"), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, with sex and uw interactions, not sex-stratified
all.adj4[[2]] <- table.mvreg(mvreg_response_nonpc, exposures.std[2], c(cell.props, covars.fem, paste0(exposures.std[2], "*uw"), "height*sex"), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, without sex interactions, with uw interaction
all.adj5[[2]] <- table.mvreg(mvreg_response_nonpc, exposures.std[2], c(cell.props, covars.fem, "height*sex"), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, without interactions

for (j in 1:length(exposures.std)) {
  all.pc.unadj.i[[j]] <- table.mvreg(mvreg_response_pc, exposures.std[j], c("sex", paste0(exposures.std[j], "*sex")), epi4, to_return = "model")
  all.pc.adj2[[j]] <- table.mvreg(mvreg_response_pc, exposures.std[j], c(paste0(exposures.std[j], "*sex"), cell.props, covars.fem), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, not uw-stratified
  all.pc.adj3[[j]] <- table.mvreg(mvreg_response_pc, exposures.std[j], c(paste0(exposures.std[j], "*sex"), cell.props, covars.fem, paste0(exposures.std[j], "*sex"), paste0(exposures.std[j], "*uw")), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, with sex and uw interactions, not sex-stratified
  all.pc.adj4[[j]] <- table.mvreg(mvreg_response_pc, exposures.std[j], c(cell.props, covars.fem, "sex", paste0(exposures.std[j], "*uw")), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, without sex interactions, with uw interaction
  all.pc.adj5[[j]] <- table.mvreg(mvreg_response_pc, exposures.std[j], c(cell.props, covars.fem, "sex"), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, without interactions
}

# adding height to the waist circumference plots.
all.pc.adj2[[2]] <- table.mvreg(mvreg_response_pc, exposures.std[2], c(paste0(exposures.std[2], "*sex"), cell.props, covars.fem, "height*sex"), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, not uw-stratified
all.pc.adj3[[2]] <- table.mvreg(mvreg_response_pc, exposures.std[2], c(cell.props, covars.fem, paste0(exposures.std[2], "*sex"), paste0(exposures.std[2], "*uw"), "height*sex"), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, with sex and uw interactions, not sex-stratified
all.pc.adj4[[2]] <- table.mvreg(mvreg_response_pc, exposures.std[2], c(cell.props, covars.fem, paste0(exposures.std[2], "*uw"), "height*sex"), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, without sex interactions, with uw interaction
all.pc.adj5[[2]] <- table.mvreg(mvreg_response_pc, exposures.std[2], c(cell.props, covars.fem, "height*sex"), epi4 %>% mutate(across(c(num.preg.comp, totmonthsbf), function (x) ifelse(is.na(x), 0, x))), to_return = "model") # fully-adjusted, without interactions

```

```{r which model 5s}

num <- length(exposures.std)*length(mvreg_response_labels)

all.final <- list(list(),list(),list(),list())

all.pc.final <- list(list(),list(),list(),list())

for (i in 1:length(exposures.std)) {
  for (j in 1:length(mvreg_response_labels)) {
    all.final[[i]][[j]] <- return.fm(return.fm(all.adj3[[i]][[j]], all.adj2[[i]][[j]], all.adj5[[i]][[j]]), return.fm(all.adj3[[i]][[j]], all.adj4[[i]][[j]], all.adj5[[i]][[j]]))
  
    all.pc.final[[i]][[j]] <- return.fm(return.fm(all.pc.adj3[[i]][[j]], all.pc.adj2[[i]][[j]], all.pc.adj5[[i]][[j]]), return.fm(all.pc.adj3[[i]][[j]], all.pc.adj4[[i]][[j]], all.pc.adj5[[i]][[j]]))
  }
}

```

```{r making s sex-stratified models for DunedinPACE, include = FALSE, eval = TRUE}

# create empty lists
# males
m.adj2 <- list() # fully-adjusted
m.adj3 <- list() # fully-adjusted, with underweight interacted

# females
f.adj2 <- list() # fully-adjusted
f.adj3 <- list() # fully-adjusted, with underweight interacted

# Male only
for (j in 1:length(exposures.std)) {
  m.adj2[[j]] <- table.mvreg(mvreg_response_nonpc[7], exposures.std[j], c(cell.props, covars.all), epi4[epi4$sex == 1,], to_return = "model") # fully-adjusted, not underweight-interacted
  m.adj3[[j]] <- table.mvreg(mvreg_response_nonpc[7], exposures.std[j], c(cell.props, covars.all, paste0(exposures.std[j], "*uw")), epi4[epi4$sex == 1,], to_return = "model") # fully-adjusted, underweight interacted
}

# adding height to waist circumference
m.adj2[[2]] <- table.mvreg(mvreg_response_nonpc[7], exposures.std[2], c(cell.props, covars.all, "height"), epi4[epi4$sex == 1,], to_return = "model") # fully-adjusted, not underweight-interacted
m.adj3[[2]] <- table.mvreg(mvreg_response_nonpc[7], exposures.std[2], c(cell.props, covars.all, paste0(exposures.std[2], "*uw"), "height"), epi4[epi4$sex == 1,], to_return = "model") # fully-adjusted, underweight interacted

# Female only
for (j in 1:length(exposures.std)) {
  f.adj2[[j]] <- table.mvreg(mvreg_response_nonpc[7], exposures.std[j], c(cell.props, covars.fem), epi4[epi4$sex == 0,], to_return = "model") # fully-adjusted, not sex-stratified
  f.adj3[[j]] <- table.mvreg(mvreg_response_nonpc[7], exposures.std[j], c(cell.props, covars.fem, paste0(exposures.std[j], "*uw")), epi4[epi4$sex == 0,], to_return = "model") # fully-adjusted, underweight interacted
}

# adding height to waist circumference
f.adj2[[2]] <- table.mvreg(mvreg_response_nonpc[7], exposures.std[2], c(cell.props, covars.fem, "height"), epi4[epi4$sex == 0,], to_return = "model") # fully-adjusted, not underweight-interacted
f.adj3[[2]] <- table.mvreg(mvreg_response_nonpc[7], exposures.std[2], c(cell.props, covars.fem, paste0(exposures.std[2], "*uw"), "height"), epi4[epi4$sex == 0,], to_return = "model") # fully-adjusted, underweight interacted

```

```{r which model 5 s sex-stratified}

num <- length(exposures.std)*length(mvreg_response_labels)

f.final <- list(list(),list(),list())
m.final <- list(list(),list(),list())

f.pc.final <- list(list(),list(),list())
m.pc.final <- list(list(),list(),list())

for (i in 1:length(exposures.std)) {
  f.final[[i]][[1]] <- return.fm(f.adj3[[i]][[1]], f.adj2[[i]][[1]])
  m.final[[i]][[1]] <- return.fm(m.adj3[[i]][[1]], m.adj2[[i]][[1]])
}

```

### Table 2 (Standardised betas, for publication) {.tabset .tabset-fade .tabset-pills}

#### Individual Clocks

##### non-PC
```{r, include = TRUE}

make_table2_pub(
    model_list = all.final,
    model_names = mvreg_response_nonpc,
    keep_betas = c("BMI", "WC", "WHtR"),
    start = 2, stop = 7
) %>% my_kable(
    col.names = c(
        "Measure", "Coeff", mvreg_response_labels[2:7]
        ),
    caption = "Unstandardised Betas"
)

full_join(
  adj_benj_hoch(
    do.call(rbind, lapply(c(1:length(exposures_pub)), function(x) extract_coef_pval(
      f.final[[x]][[1]],
      model_name = exposures_pub[x],
      to_return = c("BMI", "WC", "WHtR", "BMI*uw", "WC*uw", "WHtR*uw")
    ))), which.group2 = c("BMI", "WC", "WHtR")
  ),
  adj_benj_hoch(
    do.call(rbind, lapply(c(1:length(exposures_pub)), function(x) extract_coef_pval(
      m.final[[x]][[1]],
      model_name = exposures_pub[x],
      to_return = c("BMI", "WC", "WHtR", "BMI*uw", "WC*uw", "WHtR*uw")
    ))), which.group2 = c("BMI", "WC", "WHtR")
  ), by = c("Clock", "term")
) %>% mutate(across(everything(), ~ifelse(is.na(.), "", .))) %>% kable(col.names = c("Measure", "Coeff", "Female", "Male"), format='html', escape=FALSE) %>%
  kable_styling(bootstrap_options = "striped", full_width = F) %>%
  column_spec(column = 1, bold = TRUE) %>%
  column_spec(column = 3:4, width = "16em") %>%
  collapse_rows(columns = 1, valign = "top") %>%
  add_header_above(header = c(
    setNames(object = 2, nm = " "),
    setNames(object = 2, nm = mvreg_response_labels[7])
    ))

```

##### PC
```{r, include = TRUE}

make_table2_pub(
    model_list = all.pc.final,
    model_names = mvreg_response_pc,
    keep_betas = c("BMI", "WC", "WHtR"),
    start = 2, stop = 7
) %>% my_kable(
    col.names = c(
        "Measure", "Coeff", mvreg_response_labels_pub[2:7]
        ),
    caption = "Unstandardised Betas"
)

```

#### Combination Clocks

```{r, include = TRUE}

make_table2_pub(
    model_list = list(list(all.final[[1]][[1]], all.pc.final[[1]][[1]]), list(all.final[[2]][[1]], all.pc.final[[2]][[1]]), list(all.final[[3]][[1]], all.pc.final[[3]][[1]])),
    model_names = mvreg_response_pc,
    keep_betas = c("BMI", "WC", "WHtR"),
    start = 1, stop = 2,
    which.group2 = "none"
) %>% my_kable(
    col.names = c(
        "Measure", "Coeff", c(mvreg_response_labels[1], mvreg_response_labels_pub[1])
        ),
    caption = "Unstandardised Betas"
)

```


### Compare betas by adiposity measure {.tabset .tabset-fade .tabset-pills}
- For predictors that are statistically significant, we empirically compare them.

```{r, include = TRUE}
# cc = coefficient comparison
# BMI - all clocks
cc.BMI <- cbind(
  rbind(
    coeff_comp(all.final[[1]][[1]], all.final[[1]][[2]], predictor = "z.bmi", nested = FALSE),
    coeff_comp(all.final[[1]][[1]], all.final[[1]][[3]], predictor = "z.bmi", nested = FALSE),
    coeff_comp(all.final[[1]][[1]], all.final[[1]][[4]], predictor = "z.bmi", nested = FALSE),
    coeff_comp(all.final[[1]][[1]], all.final[[1]][[5]], predictor = "z.bmi", nested = FALSE),
    coeff_comp(all.final[[1]][[1]], all.final[[1]][[6]], predictor = "z.bmi", nested = FALSE),
    coeff_comp(all.final[[1]][[1]], f.final[[1]][[1]], predictor = "z.bmi", nested = FALSE),
    coeff_comp(all.final[[1]][[1]], m.final[[1]][[1]], predictor = "z.bmi", nested = FALSE)),
  c("Factor & Horvath", "Factor & Hannum", "Factor & PhenoAge", "Factor & GrimAge", "Factor & DNAmTL", "Factor & DunedinPACE (F, non-uw)", "Factor & DunedinPACE (M, non-uw)"))

# WC all clocks
cc.WC <- cbind(
  rbind(
    coeff_comp(all.final[[2]][[1]], all.final[[2]][[2]], predictor = "z.waist", nested = FALSE),
    coeff_comp(all.final[[2]][[1]], all.final[[2]][[3]], predictor = "z.waist", nested = FALSE),
    coeff_comp(all.final[[2]][[1]], all.final[[2]][[4]], predictor = "z.waist", nested = FALSE),
    coeff_comp(all.final[[2]][[1]], all.final[[2]][[5]], predictor = "z.waist", nested = FALSE),
    coeff_comp(all.final[[2]][[1]], all.final[[2]][[6]], predictor = "z.waist", nested = FALSE),
    coeff_comp(all.final[[2]][[1]], f.final[[2]][[1]], predictor = "z.waist", nested = FALSE),
    coeff_comp(all.final[[2]][[1]], m.final[[2]][[1]], predictor = "z.waist", nested = FALSE)),
  c("Factor & Horvath", "Factor & Hannum", "Factor & PhenoAge", "Factor & GrimAge", "Factor & DNAmTL", "Factor & DunedinPACE (F, non-uw)", "Factor & DunedinPACE (M, non-uw)"))

# WHtR all clocks
cc.WHtR <- cbind(
  rbind(
    coeff_comp(all.final[[3]][[1]], all.final[[3]][[2]], predictor = "z.whtr", nested = FALSE),
    coeff_comp(all.final[[3]][[1]], all.final[[3]][[3]], predictor = "z.whtr", nested = FALSE),
    coeff_comp(all.final[[3]][[1]], all.final[[3]][[4]], predictor = "z.whtr", nested = FALSE),
    coeff_comp(all.final[[3]][[1]], all.final[[3]][[5]], predictor = "z.whtr", nested = FALSE),
    coeff_comp(all.final[[3]][[1]], all.final[[3]][[6]], predictor = "z.whtr", nested = FALSE),
    coeff_comp(all.final[[3]][[1]], f.final[[3]][[1]], predictor = "z.whtr", nested = FALSE),
    coeff_comp(all.final[[3]][[1]], m.final[[3]][[1]], predictor = "z.whtr", nested = FALSE)),
  c("Factor & Horvath", "Factor & Hannum", "Factor & PhenoAge", "Factor & GrimAge", "Factor & DNAmTL", "Factor & DunedinPACE (F, non-uw)", "Factor & DunedinPACE (M, non-uw)"))

# Now, the PC clocks
# BMI - all clocks
cc.pc.BMI <- cbind(
  rbind(
    coeff_comp(all.pc.final[[1]][[1]], all.final[[1]][[1]], predictor = "z.bmi", nested = FALSE),
    coeff_comp(all.pc.final[[1]][[1]], all.pc.final[[1]][[2]], predictor = "z.bmi", nested = FALSE),
    coeff_comp(all.pc.final[[1]][[1]], all.pc.final[[1]][[3]], predictor = "z.bmi", nested = FALSE),
    coeff_comp(all.pc.final[[1]][[1]], all.pc.final[[1]][[4]], predictor = "z.bmi", nested = FALSE),
    coeff_comp(all.pc.final[[1]][[1]], all.pc.final[[1]][[5]], predictor = "z.bmi", nested = FALSE),
    coeff_comp(all.pc.final[[1]][[1]], all.pc.final[[1]][[6]], predictor = "z.bmi", nested = FALSE),
    coeff_comp(all.pc.final[[1]][[1]], f.final[[1]][[1]], predictor = "z.bmi", nested = FALSE),
    coeff_comp(all.pc.final[[1]][[1]], m.final[[1]][[1]], predictor = "z.bmi", nested = FALSE)),
  c("PCFactor & Factor", "PCFactor & Horvath", "PCFactor & Hannum", "PCFactor & PhenoAge", "PCFactor & GrimAge", "PCFactor & DNAmTL", "PCFactor & DunedinPACE (F, non-uw)", "PCFactor & DunedinPACE (M, non-uw)"))

# WC all clocks
cc.pc.WC <- cbind(
  rbind(
    coeff_comp(all.pc.final[[2]][[1]], all.final[[2]][[1]], predictor = "z.waist", nested = FALSE),
    coeff_comp(all.pc.final[[2]][[1]], all.pc.final[[2]][[2]], predictor = "z.waist", nested = FALSE),
    coeff_comp(all.pc.final[[2]][[1]], all.pc.final[[2]][[3]], predictor = "z.waist", nested = FALSE),
    coeff_comp(all.pc.final[[2]][[1]], all.pc.final[[2]][[4]], predictor = "z.waist", nested = FALSE),
    coeff_comp(all.pc.final[[2]][[1]], all.pc.final[[2]][[5]], predictor = "z.waist", nested = FALSE),
    coeff_comp(all.pc.final[[2]][[1]], all.pc.final[[2]][[6]], predictor = "z.waist", nested = FALSE),
    coeff_comp(all.pc.final[[2]][[1]], f.final[[2]][[1]], predictor = "z.waist", nested = FALSE),
    coeff_comp(all.pc.final[[2]][[1]], m.final[[2]][[1]], predictor = "z.waist", nested = FALSE)),
  c("PCFactor & Factor", "PCFactor & Horvath", "PCFactor & Hannum", "PCFactor & PhenoAge", "PCFactor & GrimAge", "PCFactor & DNAmTL", "PCFactor & DunedinPACE (F, non-uw)", "PCFactor & DunedinPACE (M, non-uw)"))

# WHtR all clocks
cc.pc.WHtR <- cbind(
  rbind(
    coeff_comp(all.pc.final[[3]][[1]], all.final[[3]][[1]], predictor = "z.whtr", nested = FALSE),
    coeff_comp(all.pc.final[[3]][[1]], all.pc.final[[3]][[2]], predictor = "z.whtr", nested = FALSE),
    coeff_comp(all.pc.final[[3]][[1]], all.pc.final[[3]][[3]], predictor = "z.whtr", nested = FALSE),
    coeff_comp(all.pc.final[[3]][[1]], all.pc.final[[3]][[4]], predictor = "z.whtr", nested = FALSE),
    coeff_comp(all.pc.final[[3]][[1]], all.pc.final[[3]][[5]], predictor = "z.whtr", nested = FALSE),
    coeff_comp(all.pc.final[[3]][[1]], all.pc.final[[3]][[6]], predictor = "z.whtr", nested = FALSE),
    coeff_comp(all.pc.final[[3]][[1]], f.final[[3]][[1]], predictor = "z.whtr", nested = FALSE),
    coeff_comp(all.pc.final[[3]][[1]], m.final[[3]][[1]], predictor = "z.whtr", nested = FALSE)),
  c("PCFactor & Factor", "PCFactor & Horvath", "PCFactor & Hannum", "PCFactor & PhenoAge", "PCFactor & GrimAge", "PCFactor & DNAmTL", "PCFactor & DunedinPACE (F, non-uw)", "PCFactor & DunedinPACE (M, non-uw)"))


# Factor
cc.1f <- do.call(
  rbind,
  lapply(2:3, function(x) coeff_comp(all.final[[1]][[1]], all.final[[x]][[1]], predictor = "z.bmi", predictor2 = paste0("z.", exposures[x]), nested = FALSE))
) %>% cbind(c("bmi & wc", "bmi & whtr")) %>% rbind(
  c(coeff_comp(all.final[[2]][[1]], all.final[[3]][[1]], predictor = "z.waist", predictor2 = paste0("z.", exposures[3]), nested = FALSE), "wc & whtr"))

cc.1f %>% po.kable(caption = "Factor")

# females DunedinPACE
ws.f <- cbind(
  "Clock" = mvreg_response_labels[7],
  "outcome" = mvreg_response_nonpc[7],
  "Adiposity p-value" = do.call(rbind, lapply(1:3, function(x) f.final[[x]][[1]] %>% broom::tidy() %>% filter(grepl("z.*", term)))) %>% dplyr::select(p.value) %>% min(),
  "uw-interaction" = gsub(",\\s*$", "", do.call(paste, lapply(1:3, function(x) ifelse(f.final[[x]][[1]] %>% broom::tidy() %>% dplyr::select(term) %>% grepl(":uw*", .), paste0(exposures[x], ", "), ""))))
) %>% as.data.frame() %>% mutate(across(3, as.numeric)) %>% mutate(
  comparison = case_when(
    grepl("[a-z]", `uw-interaction`) ~ "Margins",
    `Adiposity p-value` < 0.05        ~ "Compare coefficients",
    TRUE                              ~ ""
  )
)

# males DunedinPACE
ws.m <- cbind(
  "Clock" = mvreg_response_labels[7],
  "outcome" = mvreg_response_nonpc[7],
  "Adiposity p-value" = do.call(rbind, lapply(1:3, function(x) m.final[[x]][[1]] %>% broom::tidy() %>% filter(grepl("z.*", term)))) %>% dplyr::select(p.value) %>% min(),
  "uw-interaction" = gsub(",\\s*$", "", do.call(paste, lapply(1:3, function(x) ifelse(m.final[[x]][[1]] %>% broom::tidy() %>% dplyr::select(term) %>% grepl(":uw*", .), paste0(exposures[x], ", "), ""))))
) %>% as.data.frame() %>% mutate(across(3, as.numeric)) %>% mutate(
  comparison = case_when(
    grepl("[a-z]", `uw-interaction`) ~ paste0("Margins for ", `uw-interaction`),
    `Adiposity p-value` < 0.05        ~ "Compare coefficients",
    TRUE                              ~ ""
  )
)

# DunedinPACE - I know BMI shouldn't be there, but this is internal and supplementary
cc.dun.m <- do.call(
  rbind,
  lapply(2:3, function(x) coeff_comp(m.final[[1]][[1]], m.final[[x]][[1]], predictor = "z.bmi", predictor2 = paste0("z.", exposures[x]), nested = FALSE))
) %>% cbind(c("bmi & wc", "bmi & whtr")) %>% rbind(
  c(coeff_comp(m.final[[2]][[1]], m.final[[3]][[1]], predictor = "z.waist", predictor2 = paste0("z.", exposures[3]), nested = FALSE), "wc & whtr"))

cc.dun.m %>% po.kable(caption = "DunedinPACE, Males only, BMI later in margins")

# cc = coefficient comparison
# PC Single factor
cc.1f.pc <- do.call(
  rbind,
  lapply(2:3, function(x) coeff_comp(all.pc.final[[1]][[1]], all.pc.final[[x]][[1]], predictor = "z.bmi", predictor2 = paste0("z.", exposures[x]), nested = FALSE))
) %>% cbind(c("bmi & wc", "bmi & whtr")) %>% rbind(
  c(coeff_comp(all.pc.final[[2]][[1]], all.pc.final[[3]][[1]], predictor = "z.waist", predictor2 = paste0("z.", exposures[3]), nested = FALSE), "wc & whtr")
)

cc.1f.pc %>% po.kable(caption = "PCFactor")

# PC Hannum
cc.hannum.pc <- do.call(
  rbind,
  lapply(2:3, function(x) coeff_comp(all.pc.final[[1]][[3]], all.pc.final[[x]][[3]], predictor = "z.bmi", predictor2 = paste0("z.", exposures[x]), nested = FALSE))
) %>% cbind(c("bmi & wc", "bmi & whtr")) %>% rbind(
  c(coeff_comp(all.pc.final[[2]][[3]], all.pc.final[[3]][[3]], predictor = "z.waist", predictor2 = paste0("z.", exposures[3]), nested = FALSE), "wc & whtr"))

cc.hannum.pc %>% po.kable(caption = "Hannum PC")

# PC pheno
cc.pheno.pc <- do.call(
  rbind,
  lapply(c(2,3), function(x) coeff_comp(all.pc.final[[1]][[4]], all.pc.final[[x]][[4]], predictor = "z.bmi", predictor2 = paste0("z.", exposures[x]), nested = FALSE))
) %>% cbind(c("bmi & wc", "bmi & whtr")) %>% rbind(
  c(coeff_comp(all.pc.final[[2]][[4]], all.pc.final[[3]][[4]], predictor = "z.waist", predictor2 = "z.whtr", nested = FALSE), "wc & whtr")
)

cc.pheno.pc %>% po.kable(caption = "PhenoAge PC")

cc.BMI %>% po.kable(caption = "BMI | Factor (non-PC)")
cc.WC %>% po.kable(caption = "WC | Factor (non-PC)")
cc.WHtR %>% po.kable(caption = "WHtR | Factor (non-PC)")
cc.pc.BMI %>% po.kable(caption = "BMI | PCFactor")
cc.pc.WC %>% po.kable(caption = "WC | PCFactor")
cc.pc.WHtR %>% po.kable(caption = "WHtR | PCFactor")

```

### Margins for significant interactions {.tabset .tabset-fade .tabset-pills}

PhenoAA and PC PhenoAA are experimental - not due to significant interactions, but to test the effect of controlling for WBC proportions by comparing margins side-by-side.

#### DunedinPACE

```{r margins Dunedin, include = TRUE}

# DunedinPACE BMI
bmi.dun <- makes3margins(
  objects = list(all.final[[1]][[7]], f.final[[1]][[1]], m.final[[1]][[1]]),
  newdata = epi_deid2 %>%
    dplyr::select(
      mvreg_response_nonpc[7], dunedin,
      paste0("z.", exposures[1]), exposures[1],
      all_of(cell.props), cursmok, hai, num.preg.comp, totmonthsbf, uw, sex
    ),
  x_axis = exposures[1], x_range = seq(15.5, 30.5, 2), bandwidth = 1,
  y_axis = mvreg_response_nonpc[7],
  title = "DunedinPACE : BMI", x_lab = "BMI (kg/m2)", y_lab = "\u0394 DunedinPACE",
  translate = "dunedin", sd_ratio = sd(epi_deid2$dunedin)/sd(epi_deid2$rs.dunedin)
  )

# DunedinPACE WC
wc.dun <- makes3margins(
  objects = list(all.final[[2]][[7]], f.final[[2]][[1]], m.final[[2]][[1]]),
  newdata = epi_deid2 %>%
    dplyr::select(
      mvreg_response_nonpc[7], dunedin,
      paste0("z.", exposures[2]), exposures[2],
      all_of(cell.props), cursmok, hai, num.preg.comp, totmonthsbf, uw, sex, height
    ),
  x_axis = exposures[2], x_range = seq(60, 85, 5), bandwidth = 2.5,
  y_axis = mvreg_response_nonpc[7],
  title = "DunedinPACE : WC", x_lab = "WC (cm)", y_lab = "\u0394 DunedinPACE",
  translate = "dunedin", sd_ratio = sd(epi_deid2$dunedin)/sd(epi_deid2$rs.dunedin)
  )

# DunedinPACE WHtR
whtr.dun <- makes3margins(
  objects = list(all.final[[3]][[7]], f.final[[3]][[1]], m.final[[3]][[1]]),
  newdata = epi_deid2 %>%
    dplyr::select(
      mvreg_response_nonpc[7], dunedin,
      paste0("z.", exposures[3]), exposures[3],
      all_of(cell.props), cursmok, hai, num.preg.comp, totmonthsbf, uw, sex
    ),
  x_axis = exposures[3], x_range = seq(0.38, 0.53, 0.03), bandwidth = 0.015,
  y_axis = mvreg_response_nonpc[7],
  title = "DunedinPACE : WHtR", x_lab = "WHtR", y_lab = "\u0394 DunedinPACE",
  translate = "dunedin", sd_ratio = sd(epi_deid2$dunedin)/sd(epi_deid2$rs.dunedin)
  )

# print out main plots
bmi.dun[[1]] + wc.dun[[1]] + whtr.dun[[1]] + patchwork::plot_layout(nrow = 2, guides = "collect")

y_range <- lapply(append(bmi.dun, append(wc.dun, whtr.dun)), function(x) layer_scales(x)$y$range$range) %>% unlist() %>% range()

# print out the plots
collect_plots(lapply(bmi.dun, function(x) x + ylim(y_range)), ylims = FALSE)
collect_plots(lapply(wc.dun, function(x) x + ylim(y_range)), ylims = FALSE)
collect_plots(lapply(whtr.dun, function(x) x + ylim(y_range)), ylims = FALSE)

```

### Supplementary Materials {.tabset .tabset-fade .tabset-pills}

#### Supplementary goodness-of-fit tables

Using modelsummary: https://modelsummary.com/man/modelsummary.html

```{r modelsummary supplementary table2, eval = FALSE}

# unadjusted models

# non-pc, no waist circumference
lapply(c(1,3), function(x) lapply(
  1:6, function(y) modelsummary(
    list("Model 1" = all.unadj.i[[x]][[y]], "Model 2" = all.adj3[[x]][[y]], "Final Model" = all.final[[x]][[y]]),
  estimate = "{estimate} ({conf.low}, {conf.high})",
  statistic = c("Std.Error: {std.error}", "p-val: {p.value}"),
  coef_rename = c(
    "(Intercept)",
    exposures_pub[[x]],
    "Sex",
    paste0(exposures_pub[[x]], " × Sex"),
    "CD8T cells",
    "CD4T cells",
    "Natural killer cells",
    "B cells",
    "Monocytes",
    "Granulocytes",
    "Former smoker",
    "Current smoker",
    "Wealth index",
    "Completed Pregs",
    "Months breastfeeding",
    "Underweight",
    "Completed Pregs × Months breastfeeding",
    paste0(exposures_pub[[x]], " × Underweight")
    ),
  title = paste(exposures_pub[x], "|", mvreg_response_labels[y]),
  output = paste0("tables/supplementary/table1_supp/single_csvs/", exposures_pub[x], "_", mvreg_response_labels[y], ".csv")
  )
))

# non-pc, waist circumference
lapply(
  1:6, function(y) modelsummary(
    list("Model 1" = all.unadj.i[[2]][[y]], "Model 2" = all.adj3[[2]][[y]], "Final Model" = all.final[[2]][[y]]),
  estimate = "{estimate} ({conf.low}, {conf.high})",
  statistic = c("Std.Error: {std.error}", "p-val: {p.value}"),
  coef_rename = c(
    "(Intercept)",
    exposures_pub[[2]],
    "Sex",
    paste0(exposures_pub[[2]], " × Sex"),
    "CD8T cells",
    "CD4T cells",
    "Natural killer cells",
    "B cells",
    "Monocytes",
    "Granulocytes",
    "Former smoker",
    "Current smoker",
    "Wealth index",
    "Completed Pregs",
    "Months breastfeeding",
    "Underweight",
    "Height",
    "Completed Pregs × Months breastfeeding",
    paste0(exposures_pub[[2]], " × Underweight"),
    "Height × Sex", "Height × Sex"
    ),
  title = paste(exposures_pub[2], "|", mvreg_response_labels[y]),
  output = paste0("tables/supplementary/table1_supp/single_csvs/", exposures_pub[2], "_", mvreg_response_labels[y], ".csv")
  )
)

# DunedinPACE (needed to sex-stratify)
lapply(c(1,3), function(x) modelsummary(
    list("Model 1" = all.unadj.i[[x]][[7]], "Model 2" = all.adj3[[x]][[7]], "Final Model" = all.final[[x]][[7]], "Females" = f.final[[x]][[1]], "Males" = m.final[[x]][[1]]),
  estimate = "{estimate} ({conf.low}, {conf.high})",
  statistic = c("Std.Error: {std.error}", "p-val: {p.value}"),
  coef_rename = c(
    "(Intercept)", 
    exposures_pub[[x]], 
    "Sex", 
    paste0(exposures_pub[[x]], " × Sex"),
    "CD8T cells",
    "CD4T cells",
    "Natural killer cells",
    "B cells",
    "Monocytes",
    "Granulocytes",
    "Former smoker",
    "Current smoker",
    "Wealth index",
    "Completed Pregs",
    "Months breastfeeding",
    "Underweight",
    "Completed Pregs × Months breastfeeding",
    paste0(exposures_pub[[x]], " × Underweight")
    ),
  title = paste(exposures_pub[x], "|", mvreg_response_labels[7]),
  output = paste0("tables/supplementary/table1_supp/single_csvs/", exposures_pub[x], "_", mvreg_response_labels[7], ".csv")
  )
)

# DunedinPACE WC
modelsummary(
    list("Model 1" = all.unadj.i[[2]][[7]], "Model 2" = all.adj3[[2]][[7]], "Final Model" = all.final[[2]][[7]], "Females" = f.final[[2]][[1]], "Males" = m.final[[2]][[1]]),
  estimate = "{estimate} ({conf.low}, {conf.high})",
  statistic = c("Std.Error: {std.error}", "p-val: {p.value}"),
  coef_rename = c(
    "(Intercept)",
    exposures_pub[[2]],
    "Sex",
    paste0(exposures_pub[[2]], " × Sex"),
    "CD8T cells",
    "CD4T cells",
    "Natural killer cells",
    "B cells",
    "Monocytes",
    "Granulocytes",
    "Former smoker",
    "Current smoker",
    "Wealth index",
    "Completed Pregs",
    "Months breastfeeding",
    "Underweight",
    "Height",
    "Completed Pregs × Months breastfeeding",
    paste0(exposures_pub[[2]], " × Underweight"),
    "Height × Sex"
    ),
  title = paste(exposures_pub[2], "|", mvreg_response_labels[7]),
  output = paste0("tables/supplementary/table1_supp/single_csvs/", exposures_pub[2], "_", mvreg_response_labels[7], ".csv")
  )


# non-pc, no waist circumference
lapply(c(1,3), function(x) lapply(
  1:6, function(y) modelsummary(
    list("Model 1" = all.pc.unadj.i[[x]][[y]], "Model 2" = all.pc.adj3[[x]][[y]], "Final Model" = all.pc.final[[x]][[y]]),
  estimate = "{estimate} ({conf.low}, {conf.high})",
  statistic = c("Std.Error: {std.error}", "p-val: {p.value}"),
  coef_rename = c(
    "(Intercept)",
    exposures_pub[[x]],
    "Sex",
    paste0(exposures_pub[[x]], " × Sex"),
    "CD8T cells",
    "CD4T cells",
    "Natural killer cells",
    "B cells",
    "Monocytes",
    "Granulocytes",
    "Former smoker",
    "Current smoker",
    "Wealth index",
    "Completed Pregs",
    "Months breastfeeding",
    "Underweight",
    "Completed Pregs × Months breastfeeding",
    paste0(exposures_pub[[x]], " × Underweight")
    ),
  title = paste(exposures_pub[x], "|", mvreg_response_labels_pub[y]),
  output = paste0("tables/supplementary/table1_supp/single_csvs/", exposures_pub[x], "_", mvreg_response_labels_pub[y], ".csv")
  )
))

# non-pc, waist circumference
lapply(
  1:6, function(y) modelsummary(
    list("Model 1" = all.pc.unadj.i[[2]][[y]], "Model 2" = all.pc.adj3[[2]][[y]], "Final Model" = all.pc.final[[2]][[y]]),
  estimate = "{estimate} ({conf.low}, {conf.high})",
  statistic = c("Std.Error: {std.error}", "p-val: {p.value}"),
  coef_rename = c(
    "(Intercept)",
    exposures_pub[[2]],
    "Sex",
    paste0(exposures_pub[[2]], " × Sex"),
    "CD8T cells",
    "CD4T cells",
    "Natural killer cells",
    "B cells",
    "Monocytes",
    "Granulocytes",
    "Former smoker",
    "Current smoker",
    "Wealth index",
    "Completed Pregs",
    "Months breastfeeding",
    "Underweight",
    "Height",
    "Completed Pregs × Months breastfeeding",
    paste0(exposures_pub[[2]], " × Underweight"),
    "Height × Sex", "Height × Sex"
    ),
  title = paste(exposures_pub[2], "|", mvreg_response_labels_pub[y]),
  output = paste0("tables/supplementary/table1_supp/single_csvs/", exposures_pub[2], "_", mvreg_response_labels_pub[y], ".csv")
  )
)

# get files
# adjusted
my.files <- list.files('tables/supplementary/table1_supp/single_csvs')

# combine into .xlsx
tabble(
  file.list = my.files, 
  file.path = 'tables/supplementary/table1_supp/single_csvs', 
  path.to.write.to = 'tables/supplementary/table1_supp/', 
  file.name = 'tables_w_gof')

```

#### Supplementary confounders

##### Wealth

```{r wealth_adiposity_uw, eval = TRUE, include = TRUE}

# adding and comparing them

# females
epi_deid2.svy.f <- svydesign(id      = ~new_ids,
                          data    = epi_deid2[epi_deid2$sex == 0,] %>% mutate(waist = as.numeric(waist)))

tbl_svysummary(data = epi_deid2.svy.f, 
                 by =  f.uw,
    # Use include to dplyr::select variables
    include = c(
                bmi, waist, whtr, hai, hai
                ), 
   label = list(bmi ~ "BMI (kg/m2)",
                waist ~ "Waist (cm)",
                whtr ~ "Waist-height ratio",
                hai ~ "Average Lifetime Household Wealth Index",
                hai ~ "Concurrent Household Wealth Index"),
    statistic = list(all_continuous()  ~ "{mean} ({sd})"),
    digits = list(all_continuous()  ~ c(1, 1),
                  c(hai, hai, whtr) ~ c(3,3)),
    type = list(c(bmi, waist, whtr, hai, hai) ~ "continuous"),
    missing = "no"
  ) %>%
  modify_caption("Supplementary descriptive statistics (female)") %>%
  add_p(test = list(
      all_continuous() ~ "svy.kruskal.test"
    )
  )%>%
  bold_labels()%>%
    add_overall()%>%
      modify_header(label = "**Variable**", all_stat_cols() ~ "**{level}**, n = {n} ({style_percent(p)}%)")

# males
epi_deid2.svy.m <- svydesign(id      = ~new_ids,
                          data    = epi_deid2[epi_deid2$sex == 1,] %>% mutate(waist = as.numeric(waist)))

tbl_svysummary(data = epi_deid2.svy.m, 
                 by =  f.uw,
    # Use include to dplyr::select variables
    include = c(
                bmi, waist, whtr, hai, hai
                ), 
   label = list(bmi ~ "BMI (kg/m2)",
                waist ~ "Waist (cm)",
                whtr ~ "Waist-height ratio",
                hai ~ "Average Lifetime Household Wealth Index",
                hai ~ "Concurrent Household Wealth Index"),
    statistic = list(all_continuous()  ~ "{mean} ({sd})"),
    digits = list(all_continuous()  ~ c(1, 1),
                  c(hai, hai, whtr) ~ c(3,3)),
    type = list(c(bmi, waist, whtr, hai, hai) ~ "continuous"),
    missing = "no"
  ) %>%
  modify_caption("Supplementary descriptive statistics (male)") %>%
  add_p(test = list(
      all_continuous() ~ "svy.kruskal.test"
    )
  )%>%
  bold_labels()%>%
    add_overall()%>%
      modify_header(label = "**Variable**", all_stat_cols() ~ "**{level}**, n = {n} ({style_percent(p)}%)")

```

##### Smoking

```{r smoking_bioaging, eval = TRUE, include = TRUE}

# adding and comparing them

# females
epi_deid2.svy <- svydesign(id      = ~new_ids,
                          data    = epi_deid2[epi_deid2$sex == 1,] %>% filter(!is.na(cursmok)) %>% mutate(
                            waist = as.numeric(waist),
                      cursmok = case_when(
                        cursmok == 2 ~ "Current",
                        cursmok == 1 ~ "Former", TRUE ~ "Never"
                      ))
                      )

tbl_svysummary(data = epi_deid2.svy, 
                 by =  cursmok,
    # Use include to dplyr::select variables
    include = c(
                bmi, waist, whtr,
                r.dnamage,
                r.dnamagehannum,
                r.dnamphenoage,
                r.dnamgrimage,
                r.dnamtl,
                dunedin,
                r.pchorvath2, 
                r.pchannum, 
                r.pcphenoage, 
                r.pcgrimage, 
                r.pcdnamtl,
                factor.age, 
                pcfactor.age
                ), 
   label = list(bmi ~ "BMI (kg/m2)",
                waist ~ "Waist (cm)",
                whtr ~ "Waist-height ratio",
                                # clocks
                r.dnamage ~ "Horvath", 
                r.dnamagehannum ~ "Hannum", 
                r.dnamphenoage ~ "PhenoAge", 
                r.dnamgrimage ~ "GrimAge", 
                r.dnamtl ~ "DNAmTL", 
                dunedin ~ "DunedinPACE",
                r.pchorvath2 ~ "PCHorvath", 
                r.pchannum ~ "PCHannum", 
                r.pcphenoage ~ "PCPhenoAge", 
                r.pcgrimage ~ "PCGrimAge", 
                r.pcdnamtl ~ "PCDNAmTL",
                factor.age ~ "Factor", 
                pcfactor.age ~ "PCFactor"),
    statistic = list(all_continuous()  ~ "{mean} ({sd})"),
    digits = list(all_continuous()  ~ c(3, 3),
                  c(bmi, waist) ~ c(1,1)),
    type = list(c(bmi, waist, whtr,
                r.dnamage,
                r.dnamagehannum,
                r.dnamphenoage,
                r.dnamgrimage,
                r.dnamtl,
                dunedin,
                r.pchorvath2, 
                r.pchannum, 
                r.pcphenoage, 
                r.pcgrimage, 
                r.pcdnamtl,
                factor.age, 
                pcfactor.age) ~ "continuous"),
    missing = "no"
  ) %>%
  modify_caption("Adiposity and ageing by smoking satus (males)") %>%
  add_p(test = list(
      all_continuous() ~ "svy.kruskal.test"
    )
  )%>%
  bold_labels()%>%
    add_overall()%>%
      modify_header(label = "**Variable**", all_stat_cols() ~ "**{level}**, n = {n} ({style_percent(p)}%)")

```

#### Supplementary WC and parity

```{r, include = TRUE}

# adding and comparing them
epi_deid2.t1 <- epi_deid2 %>% filter(sex == 0) # getting rid of labels

epi_deid2.t1_svy <- svydesign(id = ~new_ids, data = epi_deid2.t1 %>% mutate(
  everbirth = case_when(everbirth == 0 ~ "Nulliparous", TRUE ~ "Parous")))
#####
sum.table.f <- tbl_svysummary(data = epi_deid2.t1_svy, by = everbirth,
    # Use include to dplyr::select variables
    include = c(bmi, f.bmi4cat, waist, f.waist.high, whtr, f.whtr.high, 
                dunedin, rs.dnamphenoage, rs.pcphenoage
                ), 
   label = list(bmi ~ "BMI (kg/m2)",
                f.bmi4cat ~ 'BMI Category',
                waist ~ "Waist circumference (cm)",
                f.waist.high ~ "High Waist Circumference",
                whtr ~ "Waist-height ratio",
                f.whtr.high ~ "High Waist-to-Height Ratio",
                dunedin ~ "DunedinPACE",
                rs.dnamphenoage ~ "PhenoAge",
                rs.pcphenoage ~ "PC PhenoAge"
   ),
    statistic = list(all_continuous()  ~ "{mean} ({sd})",
                     all_categorical() ~ "{n}  ({p}%)"),
    digits = list(
                  all_continuous()  ~ c(1, 1),
                  c(whtr, dunedin, rs.dnamphenoage, rs.pcphenoage) ~ c(3,3),
                  all_categorical() ~ c(0, 1)),
    type = list(c(bmi, waist, whtr) ~ "continuous"),
   # sort = list(c(colnames(epi_deid2.t1_svy)[grepl(".high", epi_deid2.t1_svy %>% colnames)], cursmok) ~ "frequency"),
    missing = "no"
  ) %>%
  modify_caption("Descriptive statistics") %>%
  add_p(test = list(
      all_continuous() ~ "svy.kruskal.test",
      all_categorical() ~ "svy.chisq.test"
    )
  ) %>%
  bold_labels()%>%
      modify_header(label = "**Variable**", all_stat_cols() ~ "**{level}**, n = {n} ({style_percent(p)}%)")

# write.csv2(sum.table.f %>% as.data.frame(), "tables/table_WC_supp_parous_f.csv")
sum.table.f


```

#### Sensitivity Analysis

```{r sensitivity calcs, include = FALSE}
source("sensitivity_analysis.R")
```

```{r print sensitivity tables, include = TRUE}

# correlations
cor.table.ic
cor.table.fac

# beta comparisons
coeff_diffs_facs
coeff_diffs_ics

```

#### Random calcs

```{r, include = FALSE}

coeff_comp(model1 = all.pc.final[[3]][[1]], model2 = all.pc.final[[3]][[2]],
           predictor = "whtr", nested = FALSE)

```
## {-}
